Paper_analyses

### 2021-07-28 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

@@

# - use IAPS data to split valence - positive negative
# - within that - compute arousal low mid high within each valence both for the iaps data and my study
# do this on a participant basis or sampleÇ? try sample first
tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample > 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

>>>>

db_full4new_stim_screen_pupil_nopract %>%
  subset(ssid_num<500)%>%
  group_by(ssid)%>%
  mutate(cor_ar_vl = cor(arousal, valence, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ssid,cor_ar_vl))+
  geom_point()+
  geom_hline(yintercept = -.75)+
  geom_hline(yintercept = -.90)
  geom_histogram()

  ggplot(aes(arousal_c, Mean_gray_z, color = ground_valence_lab))+
  geom_point()+
  ggpubr::stat_cor()

@@

```{r}
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

@@

```{r Scrap this}

# - use IAPS data to split valence - positive negative
# - within that - compute arousal low mid high within each valence both for the iaps data and my study
# do this on a participant basis or sampleÇ? try sample first
tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(ground_valence_lab, Arousal_z_by_val ))+
  # geom_point()+
  stat_summary(geom = 'pointrange')

# hpw does this relate to the original ratigs

# do this on a participant basis or sampleÇ? try sample first
tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  # group_by(stimIAPS,ground_valence_lab)%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(ValenceMean, ArousalMean_z_by_val ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
  # stat_summary(geom = 'pointrange')+
      ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(Arousal_z_by_val, valence_c))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
  # stat_summary(geom = 'pointrange')+
      ggpubr::stat_cor()

?cut
tmp.df4_full_stim_downs_jun2021_60bins$valence_self<- cut(tmp.df4_full_stim_downs_jun2021_60bins$valence, 3,
                                                          labels = c("Negative", "Neutral", "Positive"))

tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  # mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(ground_valence_lab, Arousal_z_by_val))+
  geom_point()+
  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
  stat_summary(geom = 'pointrange')+
      ggpubr::stat_cor()

  # mean center within neutral positive, neutral negative

tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos<- if_else(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab!= "More negative", TRUE, FALSE)

tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab!= "More positive", TRUE, FALSE)

tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(neutral_pos)%>%
  mutate(neutral_pos_mean_arousal = mean(ArousalMean, na.rm = TRUE),
                                         neutral_pos_sd_arousal = sd(ArousalMean, na.rm = TRUE))%>%
  mutate(neutral_pos_mean_arousal_self = mean(arousal, na.rm = TRUE),
         neutral_pos_sd_arousal_self = sd(arousal, na.rm = TRUE))%>%
  group_by(neutral_neg)%>%

  mutate(neutral_neg_mean_arousal = mean(ArousalMean, na.rm = TRUE),
                                         neutral_sd_mean_arousal = sd(ArousalMean, na.rm = TRUE)) %>%
  mutate(neutral_neg_mean_arousal_self = mean(arousal, na.rm = TRUE),
         neutral_neg_sd_arousal_self = sd(arousal, na.rm = TRUE))

# group_by()

# replace the values when neutral_pos and neutral_neg is FALSE respectivelly
# library(dplyr)
# check how many nas do we have before we start
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal))
 # FALSE   TRUE 
# 158193  13975 
tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
    mutate_at(vars(matches('^neutral_pos_.*$')), ~ 
                  replace(., neutral_pos == FALSE, NA))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal))
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal_self))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal_self))

tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
    mutate_at(vars(matches('^neutral_neg_.*$')), ~ 
                  replace(., neutral_neg == FALSE, NA))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal_self))

tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$)

```{r}
  tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(valence_c, ArousalMean ))+
  geom_point()+
  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_cor()

      tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%

      group_by(ground_valence_lab)%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(ArousalMean_z_by_val,pup_basCor ))+
  geom_point()+
      geom_smooth(method = 'lm', se = F)+
      ggpubr::stat_cor()

    tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%

      group_by(ground_valence_lab)%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(Arousal_z_by_val,pup_basCor ))+
  geom_point()+
      geom_smooth(method = 'lm', se = F)+
      ggpubr::stat_cor()
  # geom_smooth(aes(color = ground_valence_lab), method = 'lm', se = F)

    # original variable

      tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%

      group_by(ground_valence_lab)%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(pup_basCor,arousal))+
  geom_point()+
      geom_smooth(method = 'lm', se = F)+
      ggpubr::stat_cor()

  geom_smooth(aes(color = ground_valence_lab), method = 'lm', se = F)
        tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  group_by(ground_valence_lab)%>%
  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%

      group_by(ground_valence_lab)%>%
   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
  ggplot(aes(pup_basCor, ArousalMean))+
  geom_point()+
          geom_smooth(method = 'lm', se = F)+
          ggpubr::stat_cor()
  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
